Lyman-$\alpha$ photons through rotating outflows

### 2018-07-26 paper/paper.tex
lw tau in paper

>>>>

\subsection{Low optical thickness regimes}
When located in the regimes of low optical thickness, \tauh $\lesssim 4$,  the agreement of the radiative transfer simulation with the semi-analytical solution is not as accurate. In this regime, only numerical simulations can help to predict the shape of the \lya profiles. We ran a simulation with low \tauh and compared it with the semi-analytical model. As seen in Figure \ref{fig:low_tau}, the model does not fit the simulation. This creates physical restrictions on the input of our model.

\begin{figure}
	\centering
	\includegraphics[width=0.48\textwidth]{low_tau_logtau4_theta90}
	\caption{\textbf{Low optical thickness regimes}.  
		Here we fix $\tauh=10^4$. 
		The six panels correspond to $\theta=90^\circ$.
		We vary \vrot increasing from left to right and \vout increasing
		from top to bottom. 
		The thin black line corresponds to the \lya line obtained with
		CLARA without any rotation and the indicated outflow velocity.
		The thick black line corresponds to the results including both
		outflows and rotation.
		The thick gray line shows the results of modifying the pure outflow
		solution by the Doppler shift presented in Equation \ref{eq:shift_x}
		(in thin line), if there is a radiative transfer of rotation and outflows
		(thick and clear line), and if there is a radiative transfer of
		only outflows, but also a Doppler shift from the rotational
		velocity (thick and dark line).  
		\label{fig:low_tau}}
\end{figure}
